\documentclass{beamer}
\usetheme{Boadilla}
\usepackage{bibentry}
\usepackage{cmbright}
\usepackage{natbib}
\setbeamertemplate{itemize items}[circle]
\setbeamertemplate{enumerate items}[default]

\title[Euler Equations]{Thesis Proposal: Heterogeneous Preferences and the Euler Equation Implied Rate}
\author[Li]{Pearl Li}
\date{October 16, 2015}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Questions}
\begin{itemize}
\item How do the interest rates implied by the consumption Euler equation compare to observed historical interest rates when we add...
    \begin{itemize}
    \item Habit formation?
    \item Non-separability in consumption and labor?
    \item \textbf{Heterogeneous preferences?}
    \end{itemize}
\item What is the distribution of the correlation between the implied and ``true'' interest rates?
\item How do implied rates respond to monetary shocks? Is there a hump-shaped response in consumption?
\end{itemize}
\end{frame}

\begin{frame}{Motivation}
\begin{itemize}
\item Consumption Euler equation expresses intertemporal consumption choice: $$\frac{\beta E_t u'(C_{t+1})}{u'(C_t)} = \frac{1}{1+r_t}$$
\item Assumption of nearly all standard macroeconomic models
\item Has been shown many times not to fit the data!
\end{itemize}
\end{frame}

\begin{frame}{Background}
\begin{itemize}
\item \cite{canzoneri07} show a negative correlation between implied rates and money market rates, even with habit formation
\item \cite{collard11} add non-separability in consumption and labor; find a positive correlation
\item \cite{gareis13} compare to rate implied by \cite{smets07}; find positive correlation but excess volatility
\end{itemize}
\end{frame}

\begin{frame}{Representative Agent Models}
\begin{itemize}
\item Constant relative risk aversion
$$u(c_t) = \frac{c_t^{1-\gamma}}{1-\gamma}$$
\item Habit formation (non-separability in time)
$$u(c_t, c_{t-1}) = \frac{(c_t/c_{t-1}^\varphi)^{1-\gamma}}{1-\gamma}$$
\item Non-separability in consumption and leisure $$u(c_t, c_{t-1}, \ell_t) = \frac{\left[(c_t/c_{t-1}^\varphi)^\nu \ell_t^{1-\nu}\right]^{1-\gamma}}{1-\gamma}$$
\end{itemize}
\end{frame}

\begin{frame}{Heterogeneous Preferences}
\begin{itemize}
\item Heterogeneous optimizing behavior, e.g. \cite{campbell89}'s ``rule of thumb'' consumers
\item Heterogeneous time preferences $\beta$
\item Heterogeneous risk aversion $\gamma$
\end{itemize}
\end{frame}

\begin{frame}{Data}
\begin{itemize}
\item Macroeconomic time series from FRED, including:
    \begin{itemize}
    \item Real personal consumption expenditures
    \item Real personal disposable income
    \item Real GDP
    \item Average weekly hours worked (nonfarm)
    \item Effective and target federal funds rates
    \end{itemize}
\item Journal of Commerce industrial price index
\end{itemize}
\end{frame}

\begin{frame}{Empirical Analysis}
\begin{itemize}
\item Estimate VAR of consumption, leisure, inflation, etc.
\item Compute implied rates...
    \begin{itemize}
    \item With and without habit formation and consumption/leisure non-separability
    \item With rule of thumb consumers
    \item Assuming high and low versions of $\beta$ and $\gamma$
    \item Assuming some joint distribution of $(\beta, \gamma)$
    \end{itemize}
\item Correlate implied rates with ex post rates; check correlation of residual and monetary policy
\end{itemize}
\end{frame}

\begin{frame}{Empirical Analysis}
\begin{itemize}
\item Estimate distribution of correlations with Monte Carlo experiment
\item Compute impulse responses to monetary shock (target FFR)
    \begin{itemize}
    \item Does implied rate respond similarly to effective FFR?
    \item Hump-shaped response in consumption?
    \end{itemize}
\end{itemize}
\end{frame}

\bibliographystyle{econ}
\nobibliography{proposal}

\end{document}